The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2014-01-28 paper/ms.tex
edits

\label{sec:off-center}
\begin{figure}
  \includegraphics[scale=0.3]{f8.eps}
  \caption{The two small circles show the two different spherical
    off-centered emitting regions with respect to the larger spherical
    gas distribution. The angular velocity vector is
    defined to be along the $\hat{\i}$ direction (outwards the
    page). In order to study a possible anysotropy we place an
    observer along the the $\hat{\j}$ direction. The vector
    $\hat{k}_{\rm out}$ represents the outgoing direction of an
    escaping \ly photon. {\bf Si el observador esta en j, entonces las
    dos esferas no deberian estar sobre el eje k? Lo mejor es ademas
    hacer las dos circulos pequenos punteados.}
    \label{fig:OCspheres}} 
\end{figure}

@@

@@

Figure \ref{fig:OCspheres} presents the results for the $F(\mu)$
distribution for an sphere with $\tau_{\rm H}=10^{7}$ and $V_{\rm
  max}=200$\kms. The dashed and dotted lines represent the homogeneous
and central source distribution, respectively. This shows that the
level of anisotropy induced by rotation does not surpasses the $5\%$
level. We performed the same test with all the models and we do not
fina any significant anisotropic effect.

We explore other kind of anisotropy by study the effect
of radiation sources distributed with a different symmetry than the
gas. To this end we select a subset of the photons in the homogeneous
models such as they are emitted from off-centered spheres with respect
to the gas distribution.

Figure \ref{fig:OCspheres} shows the two spherical regions we
define to test for this effect. Each has a radius of $0.5R$, where $R$
is the radius of the gaseus sphere. Provided that there is an observer
located along the $\hat{j}$ direction, we pick two possible positions
to center the spheres along the $\hat{k}$ axis: $\pm C\hat{k}$. In
this configuration the emitting sphere centered on $+C\hat{k}$ moves
away from the observer and the sphere centered on $-C\hat{j}$ moves
towards the observer.

@@

The variations in the $\mu$ distribution is shown in Figure \ref{fig:muhisto},
for the Off-Center model there is a strong dependence of the 
observed flux on the relative position of an observer with $\Delta\mu\leq 25\%$.
In contrast,the central and homogeneous source distributions only show a 
weak anisotropy at the level of $\Delta\mu\leq 3\%$. The variations
in $\mu$ does not depend on the rotational velocity while increasing the optical depth $\tau_{H}$
would also increase the variation of $\Delta\mu$ up to a $15\%$.

Figure \ref{fig:OC_profiles} show the spectra for the two off-centered
spheres located at $C=\pm0.5R$.  In this case we only use photons that
have outgoing directions aligned with the observer i.e $\vert \mu \vert > 
0.9$ $\&$ $\vert \mu \vert < 1.0]$.  We do not find any asymmetry in 
the line produced by the off-center emission, the difference
 between the profiles corresponding to the spheres located at $C=-0.5R$ 
 and that ones located at $C=0.5R$ is negligible.  As in the homogeneous/
central model the line gets broader as the rotational velocity increase also 
the central part of the line becomes predominant . 
There is also a signature of possible three peaks profiles for some models ($\tau = 10^6,
V=100,200$\kms and $\tau = 10^7, V=200,300$\kms) which would be studied 
in detail in the next section.

\begin{figure*}
\includegraphics[scale=0.3]{f10.eps}
\caption{\ly profiles for the off-center positions for all of our models, Dashed/solid
  lines represents spheres centered at $-0,5R/+0.5R$ respectively.
   \label{fig:OC_profiles}} 
\end{figure*}

\begin{figure*}
\includegraphics[scale=0.3]{f11.eps}
\caption{Three-Peak profiles for three different off-center positions $C=0.25R$ (doted line), $C=0.5R$ (dashed line) \& $C=0.75R$ (solid line) and for different rotational velocities. 
   \label{fig:3p_profiles}} 
\end{figure*}

>>>>

\label{sec:off-center}
\begin{figure}
  \includegraphics[scale=0.3]{f8.eps}
  \caption{The two small circles show the two different spherical
    off-centered emitting regions with respect to the larger spherical
    gas distribution. The angular velocity vector is
    defined to be along the $\hat{\i}$ direction (outwards the
    page). In order to study a possible anysotropy we place an
    observer along the the $\hat{\j}$ direction. The vector
    $\hat{k}_{\rm out}$ represents the outgoing direction of an
    escaping \ly photon. {\bf Si el observador esta en j, entonces las
    dos esferas no deberian estar sobre el eje k? Lo mejor es ademas
    hacer las dos circulos pequenos punteados. Por otro lado, como se
    habian definido las velocidades, el eje de rotacion es el eje k}
    \label{fig:OCspheres}} 
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[scale=0.3]{f10.eps}
\end{center}
\caption{\ly profiles for the off-centered emission. Dashed/solid
  lines represents spheres centered at $-0,5R/+0.5R$ respectively.
   \label{fig:OC_profiles}} 
\end{figure*}

\begin{figure*}
\includegraphics[scale=0.3]{f11.eps}
\caption{Triple peaked profiles for three different off-center positions
  $C=0.25R$ (doted line), $C=0.5R$ (dashed line) \& $C=0.75R$ (solid
  line) and for different rotational velocities.  
   \label{fig:3p_profiles}} 
\end{figure*}

@@

Figure \ref{fig:OCspheres} presents the results for the $F(\mu)$
distribution for an sphere with $\tau_{\rm H}=10^{7}$ and $V_{\rm
  max}=200$\kms. The dashed and dotted lines represent the homogeneous
and central source distribution, respectively. This shows that the
the  anisotropy induced by rotation is at the $3\%$ level. We
performed the same test with all the models and find that the
variation in $\mu$ does not depend on the rotational velocity;
however, high optical depth values can increase the variation of
$\mu$ up to a $15\%$.

We also explore a different source of anisotropy by studying the effect
of radiation sources located in off-centered spheres with respect to
the gas distribution. Figure \ref{fig:OCspheres} shows the two
spherical regions we define to test for this effect. Each has a radius
of $0.5R$, where $R$ is the radius of the gaseus sphere. With an
observer located along the $\hat{j}$ direction, we pick two possible
positions to center the spheres along the $\hat{k}$ axis: $\pm C\hat{k}$. In
this configuration the emitting sphere centered on $+C\hat{k}$ moves
away from the observer and the sphere centered on $-C\hat{j}$ moves
towards the observer.

In this case the $\mu$ distribution is not homogeneous as shown in
Figure \ref{fig:muhisto}. The off-center emision shows a variation at
the level of $20\%$ in intensity with the angle $\Theta$. {\bf Como se
ven los plots de otras velocidades y tau? Tambien son variaciones del
20\%?}. This variation implies that that the line is more intense in
the plane perpendicular to the rotation axis.

We also explore the effects of off-centered emission in the line
morphology. Figure \ref{fig:OC_profiles} show sthe spectra for the two
off-centered emitting spheres located at $C=\pm0.5R$.  In this case we
only use photons that have outgoing directions aligned with the
observer i.e. $0.9 <\vert \mu \vert < 1.0$. We do not find any strong
asymmetry in the line morphology.

However, we find some cases where there is a possible signature of
three peaks. This is only present in some models ($\tau = 10^6,
V=100$\kms and $\tau = 10^7, V=300$\kms) and could be the result of
two competing effects: the rise in the line's center as the photons in
the photosphere escape in a single excursion and the broadening in the
two peaks as the photons closer from the center have to scatter to
escape.

@@
